Memo of meeting

### 2018-07-11 9thJuly/9thJuly.Rmd
updated results

# Mixed effect LCA with carbohydrates intake groups redefined:

@@

>>>>

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff=25%)

@@

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)

1. Not eating; 
2. Eating low carbohydrate food (energy contribution less than or equal to 25%); 
3. Eating low-to-medium carbohydrate food (energy contribution between 25% and 50%); 
3. Eating medium-to-high carbohydrate food (energy contribution between 50% and 75%); 
4. Eating high carbohydrate food (energy contribution higher or equal to 75%).

library(kableExtra)
dt <- read.csv("../Tablecsv/ModelsMixed255075.csv", header = T)
names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
dt[1,8] <- "---"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(3,7), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

dt <- read.csv("../Tablecsv/ndns_param3255075.csv", header = T)

dt_long <- dt_long %>% 
  filter(RESPCAT != 1) %>% 
  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
  mutate(HourN = as.character(VARIABLE)) %>% 
  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))

# ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 22.57%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  27.85%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 3:  49.6%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

## Visualisation of the classes by Carbohydrate eating types (3 classes)

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3")) + 
  ylim(c(0,1))
```

## Visualisation of the 7-class model

# ggthemr("fresh", layout = "scientific")

dt <- read.csv("../Tablecsv/ndns_param7255075.csv", header = T)

dt_long <- dt_long %>% 
  filter(RESPCAT != 1) %>% 
  mutate(RESPCAT = as.factor(RESPCAT)) %>% 
  mutate(Carbo = revalue(RESPCAT, c("2" = "< 25%", "3" = "25% - 50%", "4" = "50% - 75%", "5" = "> 75%"))) %>% 
  mutate(HourN = as.character(VARIABLE)) %>% 
  mutate(HourN = factor(HourN, levels = c("H0","H1" ,"H2", "H3", "H4", "H5", "H6", "H7", "H8", "H9", "H10","H11","H12","H13","H14","H15","H16","H17","H18","H19","H20","H21","H22","H23")))

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Class == "LC1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 10.64%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  15.01%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 3:  11.56%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 4:  11.31%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 5:  9.3%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC6", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 6:  9.41%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Class == "LC7", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 7:  32.7%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c( "< 25%", "25% - 50%", "50% - 75%", "> 75%")) + 
  ylim(c(0,1))
```

## Visualisation of the classes by Carbohydrate eating types (7 classes)

ggthemr("pale", layout = "scientific")

ggplot(dt_long[dt_long$Carbo == "< 25%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low carbohydarte food consumption (< 25%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "25% - 50%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Low-to-Medium carbohydarte food consumption (25% - 50%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "50% - 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Medium-to-High carbohydarte food consumption (50% - 75%) by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))

ggplot(dt_long[dt_long$Carbo == "> 75%", ], aes(y = Prob, x=HourN, group = Class, color = Class)) + 
  geom_point(size = 2) + 
  geom_line(size = 1.2) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "High carbohydarte food consumption (> 75%) probability by people in different classes", x = "Hour of the day", y = "Probability", color = "Latent classes") + 
  scale_color_discrete(labels = c("1", "2", "3", "4", "5", "6", "7")) + 
  ylim(c(0,1))
```

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 50%)

1. Not eating; 
2. ~~Eating low carbohydrate food (energy contribution less than or equal to 25%);~~
3. Eating low-to-medium carbohydrate food (energy contribution between < 50%); 
3. Eating medium-to-high carbohydrate food (energy contribution between > = 50%); 
4. ~~Eating high carbohydrate food (energy contribution higher or equal to 75%).~~

library(kableExtra)
dt <- read.csv("../Tablecsv/ModelsMixed50.csv", header = T)
names(dt) <- c("N of classes", "log-likelihood", "G^2",  "AIC", "BIC", "cAIC", "aBIC", "Entropy")
dt[1,8] <- "---"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (All data, n = 6155)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(5,7), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; cAIC, consistent AIC; Entropy, a pseudo-r-squared index.")
```

### 2018-07-11 Memo_of_meeting.Rmd
foundamentalpart read 30%
updated results

- From Professor Luigi: 
    - Can we use 1 hour window for each participant? So each person will have 24 time sequence of eating (carbohydrates) per day. 
    - **We may calculate the energy consumption per hour for each participant. And also calculate the percentage of energy that come from carbohydrate each hour. Would that be sensible?**
    - What cut-off would be appropriate to say that within that specific hour, the consumption of carbohydrates would be good or bad?

@@

>>>>

- From Professor Luigi: 
    - Can we use 1 hour window for each participant? So each person will have 24 time sequence of eating (carbohydrates) per day. 
    - **We may calculate the energy consumption per hour for each participant. And also calculate the percentage of energy that come from carbohydrate each hour. Would that be sensible?**
    - What cut-off would be appropriate to say that within that specific hour, the consumption of carbohydrates would be good or bad?
    - **Just to add that if there is a concern that too few people would have consumed CH for example at night then we can collapse the hours at night into one class as we did with Raoul, say from 11pm till 5am or from 12 till 6am.**

@@

----------

**Date and time:** 2018-07-10 14:00 - 15:00

**Main Topic:** Discuss about the preliminary results and what should we do next?

- From what we have seen from the preliminary results, maybe we should change the cut-off values to 25%, 50%, and 75% (i.e. four categories), in order to divide the previous 26% to 75% category (medium carbohydrate food/meal).

- After the above step, maybe we can further consider combining the lower two categories (< 25% and 26% to 50%) and the higher two categories (50% to 75% and > 75%).

- One possiblity of next analysis objective could be:  carb-fibre ratio and various variation of this ratio. Usually I (Dr. Suzana) would calculate how much fibre is provided for every 10g of carbohydrate for each food product. For example, a product providing 30g of carb and 15g of fibre would have a carb-fibre ratio of 10:5. It may be the case that the same rules applies to eating occasions/meals. In the past I (Dr. Suzana) usually used to calculate the ratio and then use the actual proportion within the analysis, so a fibre-carb ratio of 2-10 would expressed as 0.2, and 1-10 would be 0.1. I wonder if given that the carb value remain always constant at 10g whether we could simply use the value for the fibre 2, 1...etc

- How to use our results from mixed LCA analysis to express the variability or regularity of carbohydrate eating within a person?

(The following idea is from Chaochen Wang, not fully discussed yet.)

- After we can decide the number of classes in the study sample, maybe we can create a variable according to their change of classes during the survey. 
    - For example, if we decided to use 3 classes or maybe 4 classes. We can use the personal class change as a way to express the regularity. 
        - In this case, if for four days survey, the subject stayed in the same class, he/she can be considered as a regular eater. 
        - For the others, if they change class for more than 1 day, he/she can be considered as a irregular eater.
        - So in the sample we will separate the subjects into regular eaters or not (2 groups)
    - Another way, probably we can try to define them with less strict rules:
        - For more than half (2 in 2, 2 in 3, or >=2 in 4) survey days, if the subject managed to stay in the same class, then he/she can be defined as a regular eater.
        - Otherwise, he/she is defined as irregular eaters. 
    - The two approaches proposed here, one is more strict than the other is because there may be only small numbers of people actually stayed in the same class for all four survey days. Because with the number of latent classes increases, the probability of jumping from one class to the other will increase, in other words, the probability of staying in the same class for four days will become lower and lower.

- Survey weighting variables.    
    - There are different weighting variables in the data set.
